Emulsions Stabilized by Magnetic Ellipsoidal Particles: A Lattice Boltzmann Study

### 2025-04-13 chapters/paper1_5.tex
Changes 1. Added new lit review 2. Refined introduction and LBM methods 3. Fixed all references so that they have journals
Changes 1. Updating some refereces of analysis to link previous sections which do the same analysis to prevent repetition 2. Updating paper 2 to remove junk results
Changes 1. removed repeated analysis definitions 2. updated steinhardt definition for voronoi version 3. Increased size of some figures

@@

\begin{equation}
q_l(i) = \left( \frac{4\pi}{2l+1} \sum_{m=-l}^{l} \left| \frac{1}{N(i)} \sum_{j=1}^{n(i)} Y_{lm}(\vec{r}_{ij}) \right|^2 \right)^{\frac{1}{2}} ,
\end{equation} 
%\TODO{update formula to the one actually used}

Here, \(n(i)\) denotes the number of nearest neighbors of particle \(i\), \(\vec{r}_{ij}\) is the vector connecting the centers of particles \(i\) and \(j\), and \(m\) is an integer ranging from \(-l\) 
to \(l\) that indexes the spherical harmonic components \(Y_{lm}\). Neighbor lists are typically defined using a fixed cutoff radius around each particle, identifying nearby particles as neighbors. 
We calculate the python package Freud to calculate the bond order parameters and use a Voronoi cell to determine the particle neighborhood rather than the standard distance criterion 
\cite{ramasubramani_freud_2020,mickel_shortcomings_2013}. The Voronoi-based method avoids the need for a predefined cutoff and yields more robust neighbor definitions, particularly in disordered systems. 
Bond orientational order parameters have been widely employed to study structural transitions in colloidal and ceramic systems, including crystallization, nucleation, and glass formation 
\cite{vagberg_glassiness_2011, besseling_three-dimensional_2007, schall_structural_2007, ozawa_jamming_2012}. $q_6$ is most commonly used to identify crystal structures by matching the calculated
values to reference values for specific crystal structures such as fcc or hcp. However, Kapfer et al. pointed out that only using $q_6$ can result in false positives for amorphous systems. \cite{kapfer_jammed_2012}
Mickel et al. identified that $q_2$ vanishes for ordered crystal arrangements and is finite for disordered particle arrangements. \cite{mickel_shortcomings_2013} Therefore we report both to
characterize the particle layer.

>>>>

This section is based on work submited to the American Institude of Physics, Physics of Fluids journal.
It is reproduced from submission number \#POF25-AR-DSFD2024-03180, with the permission of AIP Publishing.

@@

\begin{equation}
% q_l(i) = \left( \frac{4\pi}{2l+1} \sum_{m=-l}^{l} \left| \frac{1}{N(i)} \sum_{j=1}^{n(i)} Y_{lm}(\vec{r}_{ij}) \right|^2 \right)^{\frac{1}{2}} ,
q_l(i) = \sqrt{ \frac{4 \pi}{2l + 1} \Sigma_{m = -l}^{l} | \Sigma_{f} \frac{A(f)}{A}, Y_{lm}(\theta_f, \phi_f) |^2 }
\label{eq:steinhardt_definition}
\end{equation}

Here $A(f)$ denotes the area of face f of the Voronoi cell around a reference particle, $A$ is the surface area of the Voronoi cell, 
$\theta_f$ and $\phi_f$ are the polar and azimuth angles of the outer normal vector connecting the reference particle to the vertex representing
an adjacent particle and $Y_{lm}$ is the spherical harmonic component. 
Neighbor lists are typically defined using a fixed cutoff radius around each particle, identifying nearby particles as neighbors. 
We calculate the python package Freud to calculate the bond order parameters and use a Voronoi cell to determine the particle neighborhood rather than the standard distance criterion 
\cite{ramasubramani_freud_2020,mickel_shortcomings_2013}. The Voronoi-based method avoids the need for a predefined cutoff and yields more robust neighbor definitions, particularly in disordered systems. 
Bond orientational order parameters have been widely employed to study structural transitions in colloidal and ceramic systems, including crystallization, nucleation, and glass formation 
\cite{vagberg_glassiness_2011, besseling_three-dimensional_2007, schall_structural_2007, ozawa_jamming_2012}. $q_6$ is most commonly used to identify crystal structures by matching the calculated
values to reference values for specific crystal structures such as fcc or hcp. However, Kapfer et al. pointed out that only using $q_6$ can result in false positives for amorphous systems. \cite{kapfer_jammed_2012}
Mickel et al. identified that $q_2$ vanishes for ordered crystal arrangements and is finite for disordered particle arrangements. \cite{mickel_shortcomings_2013} Therefore we report both to
characterize the particle layer.

### 2025-04-13 chapters/paper2.tex
Changes 1. removed repeated analysis definitions 2. updated steinhardt definition for voronoi version 3. Increased size of some figures

\section{Results}\label{sec:results_p2}
\subsection{Hysteresis curve}
\label{section:hysteresis_curve}

@@

Bijels are kinetically arrested systems whose long-term structural properties are governed by the stability and arrangement 
of the interfacial particle monolayer. Prior studies on responsive emulsions have shown that even after the removal of external 
stimuli, the microstructure often remains unchanged for extended periods due to the interfacial 
jamming of particles \cite{cui_stabilizing_2013}. Similarly, in the hysteresis experiments 
discussed earlier (Figure~\ref{fig:hysteresis_curve}), we observed that reducing or removing the magnetic field did not 
lead to a reversal of domain coarsening or particle realignment, suggesting an inherent structural resilience once the bijel 
has stabilized.

However, bijels are formed through a dynamic arrest during spinodal decomposition, and the 
particles jam in configurations that may not correspond to a thermodynamic minimum particularly when a magnetic field is 
applied during formation. Gunther et al. also showed that bijels stabilized by ellipsoidal particles exhibited timescales 
of response distinct from bijels stabilized by spherical particle due to steric effects between ellipsoidal paticles.
Therefore, this section will seek to understand to what extent the initial particle order affects the 
bijel's capacity to relax or restructure upon removal of the field. To explore this, 
we now examine the post-stimulus structural response of bijels formed under different field conditions 
\(\bar{B}_{\text{template}} = 0.0, 0.2, 0.5, 1.0\). After allowing each structure to fully stabilize under a 
constant magnetic field, we abruptly switch off the field and observe the subsequent time evolution of both the 
microstructure and interfacial particle behavior over a duration of \(t = 10^5 \Delta t\). This analysis aims to 
clarify the mechanisms that underpin the apparent irreversibility captured in the hysteresis response and further 
assess the role of processing history in bijel stability.

@@

FIgure \ref{fig:microstructure_viz-field_down} shows that in 
both cases, the bulk microstructure remains effectively unchanged over the course of the simulation, highlighting the 
kinetic stability and arrested nature of the bijel once jamming has occurred.
However, closer inspection of the interfacial particle arrangement reveals subtle but important differences. In the 
\(\bar{B}: 0.2 \rightarrow 0.0\) case, the particles retain a degree of orientational order, although slight deviations 
from the field-aligned configuration begin to emerge. In contrast, for \(\bar{B}: 1.0 \rightarrow 0.0\), where the 
initial nematic order was stronger, the system exhibits more apparent disorganization by the final time step. This 
suggests that while the jammed interface resists large-scale rearrangement, there is a gradual relaxation of particle 
orientations in the absence of the aligning field. The extent of this relaxation appears to correlate with the initial 
alignment strength, indicating that systems formed under stronger magnetic fields exhibit greater reorientation when 
the field is removed. We probe the effect of these reorientations by calculating the time evolution of the domain size
and the corresponding nematic order parameter of the particles in Figure \ref{fig:domain_size-field_down}

@@

Figure~\ref{fig:domain_size-field_down} presents the time evolution of the normalized domain size (\(L/R\)) and nematic 
order parameter (\(S\)) for bijels stabilized by oblate (left) and prolate (right) particles following the removal of an 
applied magnetic field. For all systems except oblate particle stabilized bijel with \(\bar{B}: 0.0 \rightarrow 0.0\), 
a modest degree of domain coarsening is observed. This slow, steady increase in domain size indicates that while the 
global microstructure remains largely intact, minor structural rearrangements may still occur post-stimulus, particularly 
at long timescales. This behavior is more prominent in prolate particle systems, suggesting that elongated particles 
may provide greater local flexibility for slight monolayer relaxation without disrupting the overall network.
A notable exception arises in the oblate \(\bar{B}: 0.0 \rightarrow 0.0\) case, which exhibits a sudden and pronounced 
increase in domain size at later times. This behavior is attributed not to gradual coarsening but to a domain coalescence 
event.

The nematic order parameter \(S\) for all field-removal scenarios demonstrates a consistent, order-dependent decrease over 
time. This trend suggests that in the absence of an aligning field, particles gradually relax from their field-induced 
configurations toward thermodynamically preferred orientations governed by interfacial capillary interactions. The 
magnitude of this decay correlates with the initial degree of ordering: systems formed under higher magnetic fields 
(\(\bar{B} = 0.5\) and \(1.0\)) show the most significant reduction in \(S\), reflecting a greater degree of reorientation.

These results reinforce the interpretation that bijel microstructure is resilient to field removal, with no meaningful 
reversal in domain architecture once jamming has occurred. However, the interfacial particle monolayer continues to evolve 
at the microscale, with orientation relaxation providing a residual mechanism for slow, local structural change. To determine 
whether this relaxation induces anisotropic coarsening, we next quantify the directional change in domain size and tortuosity 
using the relative change metric \(\Delta L = \frac{L_f - L_i}{L_i}\), applied separately to \(L_\perp\) and \(L_\parallel\). 
The same formulation is used to compute directional tortuosity changes, with results summarized in 
Figure~\ref{fig:domain_size_aniso-field_up}.

\begin{figure} 
\centering 
\includegraphics[scale = 0.6]{../figures/results/paper2/domain_size_aniso-field_down.png} 
\caption{Plots of the anisotropic structural response of bijels after the removal of 
         magnetic fields, by showing the relative change in directional domain size \((\Delta L)\) and tortuosity \((\Delta \tau)\) 
         as a function of \(\Delta \bar{B}\), the change in field strength from the templated to final state. Blue curves correspond 
         to bijels stabilized by oblate particles, and red curves to those stabilized by prolate particles.} 
\label{fig:domain_size_aniso-field_down} 
\end{figure}

Overall, only minor anisotropic changes in domain size and tortuosity are observed following field removal, with no consistent 
or monotonic dependence on \(\Delta \bar{B}\). This suggests that although particles may gradually relax from their field-induced 
alignment, the resulting structural rearrangements are subtle and largely isotropic at the microstructural scale. The small 
fluctuations observed in \(\Delta L\) and \(\Delta \tau\) likely reflect localized heterogeneities in the particle monolayer 
rather than coordinated, directional coarsening. These findings support the notion that once the magnetic field is removed, 
the dominant force acting on the particles is the interfacial capillary interaction, which seeks to minimize interfacial 
energy without preference for a particular direction.

Importantly, this contrasts with the structural response observed during the application of a magnetic field, where clear 
anisotropy emerged as a result of field-driven particle reorientation. Here, despite the monolayer initially being in an 
anisotropic, ordered state, the system exhibits no significant directional relaxation, underscoring the kinetic resilience 
of the jammed interface. Thus, the microstructural evolution following stimulus removal appears to be dominated by slow, 
isotropic relaxation rather than directional restructuring.To further understand the role of the capillary interactions on the 
particle monolayer, we examine the time evolution of the interface angle \(\langle \psi \rangle\).

\begin{figure} 
\centering 
\includegraphics[scale=0.6]{../figures/results/paper2/psi-field_down.png} 
\caption{Plots of the average interfacial angle $\langle \psi \rangle$  plotted against time for bijels stabilized by oblate and prolate particles
         on the left and right plots respectively. They show slight increases in $\langle \psi \rangle$ over time indicating that the particles are
         slowly tilting out of the interface, inducing the domain coarsening observed.} 
\label{fig:interface_angle-field_down} 
\end{figure}

Figure \ref{fig:interface_angle-field_down} shows that the the rate and extent of angular relaxation appear relatively insensitive to the initial degree of 
order imposed by the templating field. For oblate particles, \(\langle \psi \rangle\) increases steadily regardless of initial alignment strength, indicating that 
even highly ordered monolayers do not retain their field-imposed orientation indefinitely. Similarly, for prolate particles, although the change in 
\(\langle \psi \rangle\) is smaller in magnitude, a comparable upward trend is evident.

These results suggest that the particle monolayer continues to evolve post field-removal, driven by interfacial forces seeking to minimize the total interfacial 
energy. However, since these angular adjustments do not lead to noticeable changes in the bulk microstructure it can be 
inferred that rotational relaxation alone is insufficient to trigger further domain coarsening once jamming has occurred. This supports the conclusion that 
structural irreversibility in these systems arises primarily from the kinetic constraints imposed by jamming, rather than any residual orientational stress 
within the particle layer.

@@

In this work, we investigated how magnetic fields influence the structure and dynamics of bijels stabilized by magnetically responsive ellipsoidal particles. Motivated 
by the relevance of bijels in applications such as catalysis, membrane filtration, and drug delivery, we explored how external stimuli can enable in-situ control over 
microstructure in these systems. Using hybrid Lattice Boltzmann-Molecular Dynamics simulations, we characterized the structural response of formed bijels by investigating
the effect of applying a magnetic field and the initial microstructure on the structural response characterized. We first demonstrated that bijels subjected to increasing 
magnetic field strength exhibit hysteresis in its structural response, where the domain size increases with field application but does not revert upon field removal.

When investigating the effect of the application of magnetic fields, our results revealed that applying magnetic fields post-formation induces domain coarsening up to 5\%, with 
field-induced anisotropy dependent on particle shape. Oblate particles exhibited growth primarily in the perpendicular direction by up to 60\%, while prolate particles showed coarsening 
along the field direction up to 40\%, 
both accompanied by a decrease in tortuosity. These changes arise from particle reorientation to the field, followed by local unjamming and interfacial rearrangement before 
re-jamming occurs, as characterized using the average interface angle of the particles and the Steinhardt bond orientational order parameter.

Importantly, the extent of microstructural change scales with the difference in magnetic field strength before and after application. We found that particle alignment 
characterized via $\langle \psi \rangle$ and $\langle Q_6 \rangle$ governs domain evolution. Disordered particle layers exhibited strong field responses, while highly ordered 
templates showed minimal change, highlighting the importance of reordering on the structural response observed. In contrast, removing the magnetic field had little effect 
on bijel structure. Domain size and anisotropy remained largely unchanged, regardless of initial particle order. While minor relaxation in particle alignment was observed, 
capillary forces alone were insufficient to drive significant structural reorganization.

Together, these results identify modes of structural response that depend upon the initial ordering of particles at the interface. The first mechanism identified occurs with
disordered particle monolayers which upon application of a magnetic field, unjam facilitating domain coarsening before rejamming once the interface area matches the 
particle cross sectional area. The second mechanism occurs due to particle reorientation to the applied field when particles are nematically ordered but not ordered in the direction
of the magnetic field.

>>>>

\section{Results}\label{sec:results_p2}
\subsection{Kinetic arrest}
\label{section:hysteresis_curve}

@@

Bijels are kinetically arrested systems whose long-term structural properties are governed by the stability and arrangement 
of the interfacial particle monolayer. Prior studies on responsive emulsions have shown that even after the removal of external 
stimuli, the microstructure often remains unchanged for extended periods due to the interfacial 
jamming of particles \cite{cui_stabilizing_2013}. Similarly, when assessing the kinetic arrest of bijels shown 
in Figure~\ref{fig:hysteresis_curve}, we observed that reducing or removing the magnetic field did not 
lead to a reversal of domain coarsening or particle realignment, suggesting an inherent structural resilience once the bijel 
has stabilized.

Gunther et al. also showed that bijels stabilized by ellipsoidal particles exhibited timescales 
of response distinct from bijels stabilized by spherical particle due to steric effects between ellipsoidal particles.
Therefore, this section will seek to understand to what extent the initial particle order affects the 
bijel's capacity to relax or restructure upon removal of the field. To explore this, 
we now examine the post-stimulus structural response of bijels formed under different field conditions 
\(\bar{B}_{\text{template}} = 0.0, 0.2, 0.5, 1.0\). After allowing each structure to fully stabilize under a 
constant magnetic field, we switch off the field and observe the subsequent time evolution of both the 
microstructure and interfacial particle behavior over a duration of \(t = 10^5 \Delta t\). This analysis aims to 
clarify the mechanisms that underpin the apparent irreversibility captured in the hysteresis response and further 
assess the role of processing history in bijel stability.

@@

Figure \ref{fig:microstructure_viz-field_down} shows that in 
both cases, the bulk microstructure remains effectively unchanged over the course of the simulation, highlighting the 
kinetic stability and arrested nature of the bijel.
However, closer inspection of the interfacial particle arrangement reveals that in the
\(\bar{B}: 0.2 \rightarrow 0.0\) case, the particles retain a degree of orientational order, although slight deviations 
from the field-aligned configuration begin to emerge. In contrast, for \(\bar{B}: 1.0 \rightarrow 0.0\), where the 
initial nematic order was stronger, the system exhibits more apparent disorganization by the final time step. This 
suggests that while the jammed interface resists large-scale rearrangement, there is a gradual relaxation of particle 
orientations in the absence of the aligning field. The extent of this relaxation correlates with the initial field strength when 
the field is removed. We probe the effect of these reorientations by calculating the time evolution of the domain size
in Figure \ref{fig:domain_size-field_down}

@@

Figure~\ref{fig:domain_size-field_down} presents the time evolution of the normalized domain size (\(L/R\)) for bijels stabilized by oblate 
(left) and prolate (right) particles following the removal of an applied magnetic field. For all systems except oblate particle stabilized 
bijel with \(\bar{B}: 0.0 \rightarrow 0.0\), a modest degree of domain coarsening is observed. This slow, steady increase in domain size 
indicates that while the global microstructure remains largely intact, minor structural rearrangements may still occur post-stimulus, particularly 
at long timescales. This behavior is more prominent in prolate particle systems, suggesting that elongated particles 
may provide greater local flexibility for slight monolayer relaxation without disrupting the overall network.
A notable exception arises in the oblate \(\bar{B}: 0.0 \rightarrow 0.0\) case, which exhibits a pronounced 
increase in domain size at later times. These results reinforce the interpretation that bijel microstructure 
is resilient to field removal, with no meaningful reversal in the fluid once jamming has occurred even though local particle reorientation occurs.

@@

In this work, we investigated how magnetic fields influence the structure and dynamics of bijels stabilized by magnetically responsive ellipsoidal particles. Motivated 
by the relevance of bijels in applications such as catalysis, membrane filtration, and drug delivery, we explored how external stimuli can enable in-situ control over 
microstructure in these systems. Using hybrid Lattice Boltzmann-Molecular Dynamics simulations, we characterized the structural response of formed bijels by investigating
the effect of applying a magnetic field and the initial microstructure on the structural response characterized. We first demonstrated that bijels subjected to increasing 
magnetic field strength exhibit kinetic arrest in its structural response, where the domain size increases with field application but does not revert upon field removal.

When investigating the effect of the application of magnetic fields, our results revealed that applying magnetic fields post-formation induces domain coarsening up to 5\%, with 
field-induced anisotropy dependent on particle shape. Oblate particles exhibited growth primarily in the perpendicular direction by up to 60\%, while prolate particles showed 
coarsening along the field direction up to 40\%, both accompanied by a decrease in tortuosity. These changes arise from particle reorientation to the field, followed by 
local unjamming and interfacial rearrangement before re-jamming occurs, as characterized using the average interface angle of the particles and the 
Steinhardt bond orientational order parameter. In contrast, removing the magnetic field had little effect 
on bijel structure. Domain size and anisotropy remained largely unchanged, regardless of initial particle order. While minor relaxation in particle alignment was observed, 
capillary forces alone were insufficient to drive significant structural reorganization.

These results show that rapid reorientation of the particle stabilizers is necessary to induce structural response in bijels. This is illustrated through structural response
of bijels occurring upon application of the field, causing rapid realignment of particles to the applied field direction while slow realignment of particles away from
the field when switching the field off generated no meaningful changes in the microstructure.

### 2025-04-13 chapters/paper3.tex
Changes 1. removed repeated analysis definitions 2. updated steinhardt definition for voronoi version 3. Increased size of some figures

Given that magnetic fields can modify the local arrangement of ellipsoidal particles at fluid interfaces, understanding how this arrangement evolves under 
different processing conditions is essential for interpreting the mechanical 
behavior observed. In particular, the contrasting effects seen for prolate and oblate particles, where increased magnetic ordering leads to a larger
and smaller yield stress respectively. To quantitatively assess the local arrangement of particles at the interface, we compute the ensemble-averaged 
Steinhardt bond orientational order parameters $q_2$ and $q_6$. 
\cite{steinhardt_bond-orientational_1983, lechner_accurate_2008, mickel_shortcomings_2013}. These parameters characterize the local structural ordering by 
projecting the orientations of neighboring particles onto spherical harmonics of degree \(l\), and are defined as

\begin{equation}
q_l(i) = \left( \frac{4\pi}{2l+1} \sum_{m=-l}^{l} \left| \frac{1}{N(i)} \sum_{j=1}^{n(i)} Y_{lm}(\vec{r}_{ij}) \right|^2 \right)^{\frac{1}{2}} ,
\end{equation} 
%\TODO{update formula to the one actually used}

Here, \(n(i)\) denotes the number of nearest neighbors of particle \(i\), \(\vec{r}_{ij}\) is the vector connecting the centers of particles \(i\) and \(j\), 
and \(m\) is an integer ranging from \(-l\) to \(l\) that indexes the spherical harmonic components \(Y_{lm}\). Neighbor lists are typically defined using a 
fixed cutoff radius around each particle, identifying nearby particles as neighbors. We calculate the python package Freud to calculate the bond order parameters 
and use a Voronoi cell to determine the particle neighborhood rather than the standard distance criterion \cite{ramasubramani_freud_2020,mickel_shortcomings_2013}. 
The Voronoi-based method avoids the need for a predefined cutoff and yields more robust neighbor definitions, particularly in disordered systems. Bond 
orientational order parameters have been widely employed to study structural transitions in colloidal and ceramic systems, including crystallization, nucleation, 
and glass formation \cite{vagberg_glassiness_2011, besseling_three-dimensional_2007, schall_structural_2007, ozawa_jamming_2012}. $q_6$ is most commonly used 
to identify crystal structures by matching the calculated values to reference values for specific crystal structures such as fcc or hcp. We plot the change in 
$q_6$ of the microstructures as a function of the processing applied in Figure \ref{fig:q6_rheology_init}

@@

\begin{figure} 
    \centering 
    \includegraphics[scale=0.3]{../figures/results/paper3/theta_z-time_compare-specific.png} 
    \caption{Comparisons of the average orientation of particles to the direction of the applied shear for bijels stabilized by
             ellipsoidal particles as a function of the applied shear rate for bijels made with no field and a field strength of $\bar{B} = 1$,
             keeping the field strength the same. We show that the orientation of particles to the applied shear is dependent on the
             applied shear rate, particle ordering to the field and the particle shape.} 
    \label{fig:theta_z_specific} 
\end{figure}

@@

As the particles are adsorbed onto the interface, there is an open question whether the reorientation of particles to the shear also causes the interface to move with the
particles. To analyze this effect, we analyzed the angle between each particles symmetry axis and the local interface normal by generating a mesh of the interface using the marching 
cubes algorithm and, for each particle, identified the nearest mesh vertex (excluding those beyond the length of the particle's long axis). We then calculated 
the angle $\psi$ between the particle orientation vector \(\hat{\vec{o}}_i\) and the local surface normal. The time evolution of the average interface
angle of all particles $\langle \psi \rangle$, calculated as a numerical average of $\psi$ for all particles, is shown in Figure~\ref{fig:interface_angle_shear}.

\begin{figure} 
    \centering 
    \includegraphics[scale=0.3]{../figures/results/paper3/psi-time_compare-specific.png} 
    \caption{Comparisons of the average orientation of particles to the interface for bijels stabilized by
             ellipsoidal particles as a function of the applied shear rate for bijels made with no field and a field strength of $\bar{B} = 1$,
             keeping the field strength the same. We show that the particles tilt out of the interface upon application of shear with the degree of
             interfacial tilting a function of the initial particle order and particle shape.} 
    \label{fig:interface_angle_shear} 
\end{figure}

>>>>

Given that magnetic fields can modify the local arrangement of ellipsoidal particles at fluid interfaces, understanding how this arrangement evolves under 
different processing conditions is essential for interpreting the mechanical 
behavior observed. In particular, the contrasting effects seen for prolate and oblate particles, where increased magnetic ordering leads to a larger
and smaller yield stress respectively. To quantitatively assess the local arrangement of particles at the interface, we compute the ensemble-averaged 
Steinhardt bond orientational order parameters $q_2$ and $q_6$. 
\cite{steinhardt_bond-orientational_1983, lechner_accurate_2008, mickel_shortcomings_2013}. The technique to calculate this parameter is provided in
Equation \ref{eq:steinhardt_definition} We plot the change in 
$\langle Q6 \rangle$ of the microstructures as a function of the processing applied in Figure \ref{fig:q6_rheology_init}

@@

\begin{figure} 
    \centering 
    \includegraphics[scale=0.5]{../figures/results/paper3/theta_z-time_compare-specific.png} 
    \caption{Comparisons of the average orientation of particles to the direction of the applied shear for bijels stabilized by
             ellipsoidal particles as a function of the applied shear rate for bijels made with no field and a field strength of $\bar{B} = 1$,
             keeping the field strength the same. We show that the orientation of particles to the applied shear is dependent on the
             applied shear rate, particle ordering to the field and the particle shape.} 
    \label{fig:theta_z_specific} 
\end{figure}

@@

As the particles are adsorbed onto the interface, there is an open question whether the reorientation of particles to the shear also causes the interface to move with the
particles. To analyze this effect, we analyzed the angle between each particles symmetry axis and the local interface, calculated in the technique described in Chapter 4.
The time evolution of the average interface angle of all particles $\langle \psi \rangle$, calculated as a numerical average of $\psi$ for all particles, is shown in 
Figure~\ref{fig:interface_angle_shear}.

\begin{figure} 
    \centering 
    \includegraphics[scale=0.5]{../figures/results/paper3/psi-time_compare-specific.png} 
    \caption{Comparisons of the average orientation of particles to the interface for bijels stabilized by
             ellipsoidal particles as a function of the applied shear rate for bijels made with no field and a field strength of $\bar{B} = 1$,
             keeping the field strength the same. We show that the particles tilt out of the interface upon application of shear with the degree of
             interfacial tilting a function of the initial particle order and particle shape.} 
    \label{fig:interface_angle_shear} 
\end{figure}
